---
title: "DS412LabFinal"
author: 'Name: Md. Nasif Sarwar'
date: "Student ID: 203-35-3133"
output:
  word_document: default
  pdf_document: default
---
```{r}
library(ggplot2)
library(DescTools)
library(geomtextpath)
library(ggcorrplot)
```

Answer to the question "UNDERSTANDING AND ANALYSIS"
                        I
                        
By analyzing the data we can see that this dataset is not proper
for visulization. Most of the feature has outliers and uneven data
for instance we can take price mean is 142 and median is 101
but the maximum value is 10000 most of the features are same
filed with outliers few of them are okay to use. 
```{r}
dataSet <-read.csv("NYCAirBnb.csv")
dataSet <- na.omit(dataSet)
head(dataSet)
```

```{r}
numeric_df<- dataSet[, !(names(dataSet) %in% c("id", "name","host_id","host_name","neighbourhood_group","neighbourhood","room_type","last_review"))]

print("For Numeric Features")
summary(numeric_df)
```
 
                            II
 Created one function to compute mode of categorical data.

  infoCategoricalData - This function takes column name as a parameter 
  and simply print mode and frequency of that feature. 
```{r}
infoCategoricalData<- function(columnName){
 cat(sprintf("\n Information of: %s\n", columnName))
print(DescTools::Mode(dataSet[,columnName]))
}

```


```{r}
print("For Categorical Features")
infoCategoricalData('name')
infoCategoricalData('host_name')
infoCategoricalData('neighbourhood_group')
infoCategoricalData('neighbourhood')
infoCategoricalData('room_type')
infoCategoricalData('last_review')
```
Answer to the Question "IMPLEMENTATION"
            I & II


                           (a)            
Histogram: This is showing us the number of available rooms
in a year a accordind to room types
2 features used
1. availability_365
2. room_type
x-axis shows the availability
y-axis shows the count or frequency
Histogram is grouped into 3 room types
```{r}
  ggplot( dataSet,aes(x=availability_365, fill=room_type)) +
    geom_histogram(binwidth= 30,color="#e9ecef", alpha=0.6, position = 'identity') +
    scale_fill_manual(name= "Room Type",values=c("#E30429", "#22F47B","#7BE5FF")) +
    labs(title = "Histogram of availability according to room type", x="Availability", y= "Frecuency")+
    theme_classic()
```
                             (b)
Density Plot: This is showing us the density of available room
in each neighborhood group. 
2 features used
1. availability_365
2. neighbourhood_group
x-axis shows the availability
y-axis shows the density
Density plot is grouped into 5 neighborhood groups.
```{r}
ggplot(dataSet,aes(x=availability_365, group=neighbourhood_group, fill=neighbourhood_group)) +
    geom_density(position="fill")+
  scale_fill_manual(name= "Neighbourhood Group",values=c("#E30429", "#22F47B","#7BE5FF","#A00E86","#A307F1"))+
  labs(title = "Density plot of availability according to neighborhood group", x="Availability", y= "Density") +
   theme_classic()
    
```
                      (c)
Box plot-This is showing us the data summery of
each neighborhood group according to availability. 
2 features used
1. availability_365
2. neighbourhood_group
x-axis shows shows the density
y-axis the availability
Box plot is grouped into 5 neighborhood groups.
```{r}
ggplot(dataSet, aes( neighbourhood_group ,  availability_365)) + 
  geom_boxplot(fill= "#81F5AD")+
    labs(title = "Boxplot of availability according to neighbourhood group", x="Neighbourhood Group", y= "Availability") +
   theme_classic()

```
Box plot-This is showing us the data summery of
each room type according to availability. 
2 features used
1. availability_365
2. room_type
x-axis shows the availability
y-axis shows  the room type 
Box plot is grouped into 3 room types
```{r}
#boxplot(data$availability_365 ~ data$room_type , ylab="sickness" , col="#69b3a2", boxwex=0.5 , main="")
ggplot(dataSet, aes( availability_365 ,  room_type)) + 
  geom_boxplot(fill= "#7009DE", col="#69b3a2")+
  labs(title = "Boxplot of availability according to room type", x="Availability", y= "Room Type") +
   theme_classic()
  
```
                                (d)
Scatter Plot- This shows the longitude and latitude according to 
neighborhood group. This represents like a map which is a fun fact
because longitude and latitude represents location.
3 features used
1. longitude
2. latitude
3. neighbourhood_group
x-axis shows the longitude
y-axis shows  the latitude 
Scatter plot is grouped into 5 neighborhood groups
which is clearly representend and looks like a map.

```{r}
ggplot(dataSet , aes(x=longitude, y=latitude, shape=neighbourhood_group, color=neighbourhood_group)) + 
    geom_point()  +
  geom_labelsmooth(aes(label = neighbourhood_group), fill = "white",
                method = "lm", formula = y ~ x,
                size = 3, linewidth = 1.5, boxlinewidth = 0.4)+
  labs(title = "Scatter plot of neighborhood group which represents map", x="Longitude", y= "Latitude",
        shape = "Neighborhood Group", color = "Neighborhood Group") +
   theme_classic()
```
                      (e)
Heat map-Room which are more avalaible or stays empty does not
gets enough reviews
3 features used
1. neighbourhood_group
2. calculated_host_listings_count
3. reviews_per_month
x-axis shows the Neighborhood
y-axis shows  the Total host listings
```{r}
ggplot(dataSet, aes(neighbourhood_group, calculated_host_listings_count  )) + 
  geom_tile(aes(fill= reviews_per_month))+
  labs(title = "Heat map of neighborhood and total host listing which has reviews per month",
       x="Neighborhood Group", y= "Total Host listing", fill="Reviews Per Month")+
  theme_classic()
```
                          (f)
Stacked Bar Chart- Neighbourhood Group availablity according to room type
3 features used
1. neighbourhood_group
2. availability_365
3. room_type
x-axis shows the Room type
y-axis shows  the frequency of availability
stacks are grouped using neighborhood group
```{r}
ggplot(dataSet, aes(fill=neighbourhood_group, y=availability_365, x=room_type)) + 
    geom_bar(position="stack", stat="identity")+
    labs(title = "Neighbourhood Group availablity according to room type.",
       x="Room Type", y= "Availability Frequency", fill= "Neighborhood Group")+
     theme_classic()
```
                               (g)
Grouped Bar Chart- Price in each neighborhood group based on room type
3 features used
1. neighbourhood_group
2. price
3. room_type
x-axis shows the price 
y-axis shows the Room type
```{r}
ggplot(dataSet, aes(fill= neighbourhood_group, price,room_type  )) + 
  geom_bar(position = "dodge", stat= "identity")+
  labs(title = "Grouped bar chart of room type according to price",
       x="Price", y= "Room Type", fill= "Neighborhood Group")+
     theme_classic()
```
 Answer to the Question "Accuracy"
 Showing strong correlation from this dataset
 
 Here I took the dataset and inserted to a new one named cor_df
 where I have all the numeric data
```{r}
cor_df<- dataSet[, !(names(dataSet) %in% c("id", "name","host_id","host_name","neighbourhood_group","neighbourhood","room_type","last_review"))]
```
Later we calculated all the correlation of the numeric features
```{r}
cor_df<- round(cor(cor_df),3)
cor_df
```
Using ggcorrplot we plotted all the correlation with values inside
generation a correlation matrix
Where top 3 correlation are:
1. Number of reviews-Reviews per month
2. Availability 365-Number of reviews 
3. Availability 365-Number of host listing
```{r}
ggcorrplot(cor_df,hc.order = TRUE, title="", lab=TRUE, lab_size =2.5 )
```